---
title: "Coursera Plotly Demo"
author: "Michael Coote"
date: "1/20/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA)
library(tidyverse)
library(plotly)
library(kableExtra)
```

## R Plotly

This is an R Markdown Ioslides presentation that provides a demo of the Plotly
graphing package. It was created as a requirment for the Johns Hopkins Coursera
Data Science Specialization.

The mtcars data set will be used for the demo. The relationship between
manual and automatic transmission to miles per gallon (mpg) will be illustrated
for the demo.

## Cars by Transmission Type

The number of cars in the dataset broken down by transmission type:
```{r cars}
mtcars$cyl <- factor(mtcars$cyl)
mtcars$vs <- factor(mtcars$vs)
mtcars$am <- factor(mtcars$am,labels=c("Automatic","Manual"))
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)

table(mtcars$am) %>% kable(col.names = c("Transmission", "Frequency"))

```

## MPG Boxplot
The manual transmission, with a median of 
**`r round(median(mtcars$mpg[mtcars$am == 'Manual']), 1)` MPG**, has the clear 
advantage.
```{r boxplot}

plot_ly(y = mtcars$mpg[mtcars$am == 'Manual'], 
        type = "box", name = "Manual") %>%
  add_trace(y = mtcars$mpg[mtcars$am == 'Automatic'], name = "Automatic")
```



